ForestClaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-02-26 docs/parco13/abstract.tex
Add a todo

To enable hardware acceleration for parallel dynamic AMR, we like to build upon
the forest-of-octrees paradigm because of its low overhead and proven
scalability \cite{BursteddeWilcoxGhattas11}.  As an important extension, we go
beyond the traditional high-order element and define each mesh element to be a
dense compute patch with $m^d$ DOFs.  In fact, this approach resembles
block-structured AMR \cite{ColellaGravesKeenEtAl07}
% todo cite John B.\ Bell
except that the patches are not overlapping, which enables us to capitalize on
our previous experience with scalable FE solvers for PDEs
\cite{BursteddeStadlerAlisicEtAl13}.  A particular implementation of such a
patch is available with the Clawpack software \cite{LeVeque97} that has been
designed to solve hyperbolic conservation laws on a uniform compute patch and
successfully used in the context of block-structured AMR \todo{AMRClaw
citation}.

>>>>

To enable hardware acceleration for parallel dynamic AMR, we like to build upon
the forest-of-octrees paradigm because of its low overhead and proven
scalability \cite{BursteddeWilcoxGhattas11}.  As an important extension, we go
beyond the traditional high-order element and define each mesh element to be a
dense compute patch with $m^d$ DOFs.  In fact, this approach resembles
block-structured AMR \cite{ColellaGravesKeenEtAl07}
\todo{favorite BoxLib citation}
except that the patches are not overlapping, which enables us to capitalize on
our previous experience with scalable FE solvers for PDEs
\cite{BursteddeStadlerAlisicEtAl13}.  A particular implementation of such a
patch is available with the Clawpack software \cite{LeVeque97} that has been
designed to solve hyperbolic conservation laws on a uniform compute patch and
successfully used in the context of block-structured AMR \todo{AMRClaw
citation}.
